\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-07-01 AffineLieAlgebras/InformalNotes/article.tex
Mergerd V.D. changes

We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations. In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of characters and states.

@@

\begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
\begin{proof} It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
\end{proof}
\end{note}
\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ constructed as the affine extension of the special embedding $A_1\subset A_2$ with the embedding index $x_e=4$. The level of the representations of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the modules of the subalgebra is equal $\tilde{k}=kx_e=4$.

@@

Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$  with the corresponding values of the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details. Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.

The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure \ref{fig:affine_A2_anom_point} up to the sixth grade. The weights $\omega (w_0+\rho)-\rho$ is shown as cross if $\epsilon(\omega)=1$ and by diamond if $\epsilon(\omega)=-1$. Simple roots of classical subalgebra $A_2$ are shown in grey and grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.

@@

The next step is to project the anomalous weights to $P_{\hat A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

We see that inside $\bar{C}_{\hat{A}_1}$, which is shown in the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

\subsubsection{Embedding of semisimple subalgebras}
\label{sec:embedd-semis-subalg}

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$. Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted in the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.

\begin{figure}[h!tb]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
    \hfill
    \caption{Representation for the special embedding  $A_1\oplus A_1\subset A_3$}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.pdf}
    \hfill
    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}

Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
They are depicted in the Figure \ref{fig:A1+A1-A3}.

This embedding is characterised by the embedding indices $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

@@

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our calculations by the first 5 grades.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.

The diagrams for  $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_1}_{\hat A_3}$ are similar to that of $L^{w_2}_{\hat A_3}$.

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}. The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

 We get the following branching rules
 \begin{equation}
   \label{eq:39}
   \begin{array}{ll}
     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
   \end{array}
 \end{equation}

Now we can obtain modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
\begin{multline}
  \label{eq:40}
  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
\end{multline}

We have chosen this example to illustrate the mechanism of out algorithm. 
In this case the modules could be reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras. We must stress that our method is universal and can be applied for an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.

@@

Another natural setting where the reduction problem for affine Lie algebras appears is the coset construction of rational conformal field theories \cite{Goddard198588}. Coset models are tightly connected with the gauged WZW-models and are actively studied in string theory especially in string models on anti-de-Sitter space \cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}. The characters of the coset model are connected with the branching functions,
\begin{equation}
  \label{eq:31}
  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
\end{equation}
where
\begin{equation}
  \label{eq:46}
  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
\end{equation}

The problem of the branching functions construction in the coset models was considered in the papers \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}. It was shown that the branching functions results in cumbersome calculations. In what follows we shall demonstrate that these calculations can be simplified by applying the injection fan method.

Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection $A_1 \to  B_2$.
Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.

The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the level of the weight and the fourth is the grade.

The set of the anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}. In the grade 0 it is exactly the set of the anomalous weights for the embedding of the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}. The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise. Simple roots of classical subalgebra $B_2$ are indicated by grey arrows while the grey diagonal plane is the Cartan subalgebra of the embedded algebra $\hat{A}_1$.

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted in the Figure \ref{fig:B2_A1}}.
  \label{fig:affine_B2_anom_point}
\end{figure}

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

>>>>

We demonstrate that our algorithm can be used in the study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some physical limitations. In the study of the coset construction of rational conformal field theory the algorithm is useful for the computation of the characters and states.

@@

\begin{note} The orthogonal subalgebra $\mathfrak{a}_{\bot}$ is always empty for the conformal embeddings $\mathfrak{a}\subset \mathfrak{g}$.
\begin{proof} It can be seen from the following consideration. In the case of the conformal embedding energy-momentum tensors are to be equal (\ref{eq:2}).
The energy-momentum tensor can be expanded into the modes $L_n$
\begin{equation}
\label{eq:47}
  T(z)=\frac{1}{2(k+h^v)}\sum_n z^{-n-1}L_n
\end{equation}
The modes are constructed as the combination of normally-ordered products of the generators of $\mathfrak{g}$.
\begin{equation}
\label{eq:48}
  L_n=\frac{1}{2(k+h^v)}\sum_a\sum_m:X^a_m X^a_{n-m}:
\end{equation}
The substitution of the generators of the algebra $\mathfrak{a}$  in terms of the generators of $\mathfrak{g}$ into these combinations of $T_{\mathfrak{a}}$ should give the energy-momentum tensor $T_{\mathfrak{g}}$. But if the set of the generators $\Delta_{\bot}$ is not empty it is not possible, since $T_{\mathfrak{g}}$ contains the combinations of the generators $X^{\alpha}_n, \; \alpha\in \Delta_{\bot}$, which can not be obtained in the expansion of components of $T_{\mathfrak{a}}$.
\end{proof}
\end{note}
\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the case where both $\mathfrak{g}$ and $\mathfrak{a}$ are affine Lie algebras:
$\hat{A}_1 \longrightarrow \hat{A}_2$ and the injection is the affine extension of the
special injection $A_1 \longrightarrow A_2$ with the embedding index $x_e=4$.
As far as the $\mathfrak{g}$-modules to be considered are of level one,
the $\mathfrak{g}$-modules will be of level $\tilde{k}=kx_e=4$.

@@

Using the definition (\ref{fan-defined})  we construct the fan $\Gamma_{\hat A_1\to\hat A_2}$
and the function $s(\gamma+\gamma_0)$ (see the Figure \ref{fig:AffineA2A1Fan}).

\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineA2_A1_fan.pdf}
  \caption{The fan and $s(\gamma+\gamma_0)$ for $\hat{A_1}\longrightarrow \hat{A_2}$}
  \label{fig:AffineA2A1Fan}
\end{figure}

Let us consider the module $L^{w_0=(0,0;1;0)}$. Here we use the (finite part; level; grade)
presentation (see section(\ref{sec:notation})) of the highest weight and the finite part
coordinates are the Dynkin indices.

The set $\widehat{\Psi^{(w_0)}}$  is depicted in the Figure
\ref{fig:affine_A2_anom_point} up to the sixth grade.
The weights $\omega (w_0+\rho)-\rho$ are marked by crosses when $\epsilon(\omega)=1$ and
by diamond when $\epsilon(\omega)=-1$. Simple roots of the classical subalgebra $A_2$ are
grey and the grey diagonal plane corresponds to the Cartan subalgebra of
the embedded algebra $\hat{A}_1$.

@@

The next step is to project the anomalous weights to $P_{\hat A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}
There we see that inside the chamber $\bar{C}_{\hat{A}_1}$, which is isolated in the
Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights
both with multiplicities 1.
These are the highest weights of the $\mathfrak{a}$-submodules and their branching
coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

\subsubsection{Embeddings of semisimple subalgebras}
\label{sec:embedd-semis-subalg}

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where
$\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$,
which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$.
To construct this injection we use the method presented in \cite{vasilevich1986method}.
We start with the 4-dimensional module $L_{A_1\oplus A_1}^{(1,1)}$.
Its diagram $\mathcal{N}_{A_1\oplus A_1}^{(1,1)}
= \left\{\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)\right\}$
is presented in Figure \ref{fig:A_1+A_1_to_A3}.

\begin{figure}[h!tb]
  \begin{multicols}{2}
    \hfill
    \includegraphics[width=50mm]{A_1+A_1_to_A3.pdf}
    \hfill
    \caption{The special embedding  $A_1\oplus A_1\subset A_3$ is based on this module}
    \label{fig:A_1+A_1_to_A3}
    \hfill
    \includegraphics[width=50mm]{A1+A1-A3.pdf}
    \hfill
    \caption{Embedded roots for the special embedding  $A_1\oplus A_1\subset A_3$}
    \label{fig:A1+A1-A3}
  \end{multicols}
\end{figure}

For the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in
the Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}
{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},
\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}
{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method},
thus $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.
The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
(See Figure \ref{fig:A1+A1-A3}.)

This injection is characterised by the embedding indices $(2,2)$ and is conformal,
since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

@@

For the sets of positive roots $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ we have
\begin{equation}
  \label{eq:38}
  \begin{array}{lll}
    \Delta^{+} &=&\left\{\co{\Delta}^{+}=\{\tilde{\alpha}_1, \tilde{\alpha}_2, \tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2, \tilde{\alpha}_2+\tilde{\alpha}_3, \tilde{\alpha}_1+\tilde{\alpha}_2+\tilde{\alpha}_3\};\right.\\
    &\; & \quad\left.\co{\Delta}+n\delta;\;     +n\delta\;\mbox{with multiplicity}\; 3;\; n=1,2,\dots,\right\}\\
    \Delta_{\mathfrak{a}}^{+} &=& \{  \alpha_1,\alpha_2;\;\pm \alpha_1+n\delta,\pm \alpha_2+n\delta;\; +n\delta\; \mbox{with multiplicity} \; 2;\; n=1,2,\dots\}\\
  \end{array}
\end{equation}
The set $\Delta^{+}_{\bot}$ is empty.
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}.
The coordinates of fan element finite part are given in the basis of $A_1\oplus A_1$ fundamental roots.
The fan elements $\gamma$ are marked by crosses if  $s(\gamma)=1$ and by diamonds if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{The fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our calculations by the first 5 grades.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set of anomalous weights $\widehat{\Psi_{\hat A_3}^{(\mu)}}$
and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for
$\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}.
Coordinates of the finite part are given in the basis of fundamental weights of $A_1\oplus A_1$.
The weights are marked by crosses if $\epsilon(\omega)=1$ and by diamonds otherwise.

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}.
Inside the chamber $\bar{C_{\mathfrak{a}}}$ the anomalous branching coefficients coinside with
the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$
and are marked by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

Treating analogously the modules $L^{w_0}_{\hat A_3}, L^{w_1}_{\hat A_3}, L^{w_3}_{\hat A_3}$
we get the following set of branching rules
 \begin{equation}
   \label{eq:39}
   \begin{array}{ll}
     L^{(0,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)} \\
     L^{(1,0,0;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\
     L^{(0,1,0;1;0]}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & \left( L_{\hat{A_1}}^{(2;2;0)}\otimes L_{\hat{A_1}}^{(0;2;0)}\right) \oplus \left( L_{\hat{A_1}}^{(0;2;0)}\otimes L_{\hat{A_1}}^{(2;2;0)}\right) \\
     L^{(0,0,1;1;0)}_{\hat{A_3}\downarrow \hat{A_1}\oplus \hat{A_1}}= & L_{\hat{A_1}}^{(1;2;0)}\otimes L_{\hat{A_1}}^{(1;2;0)} \\     
   \end{array}
 \end{equation}

Now we can construct the modular invariant partition function for WZW-model with the chiral algebra $\hat{A}_1\oplus \hat{A}_1$.
\begin{multline}
  \label{eq:40}
  Z=\left|\chi_{(0;2;0)}\chi_{(0;2;0)}\right|^2+2\left|\chi_{(1;2;0)}\chi_{(1;2;0)}\right|^2+ \left|\chi_{(2;2;0)}\chi_{(0;2;0)}+\chi_{(0;2;0)}\chi_{(2;2;0)}\right|^2=\\
  \left|\chi_{(0;2;0)}\right|^4+2\left|\chi_{(1;2;0)}\right|^4+ 4\left|\chi_{(2;2;0)}\chi_{(0;2;0)}\right|^2
\end{multline}

By this example we have illustrated the mechanism of our algorithm.
We want to remind that the proposed method is universal and can be applied to
an arbitrary pair of affine Lie algebras $\mathfrak{a}\subset\mathfrak{g}$.

@@

Another natural setting where the reduction problem for affine Lie algebras appears is
the coset construction in rational conformal field theories \cite{Goddard198588}.
Coset models are tightly connected with the gauged WZW-models and are actively studied
in string theory especially in string models on anti-de-Sitter space
\cite{Maldacena:2000hw,Maldacena:2000kv,Maldacena:2001km,Maldacena:2001ky,Aharony:1999ti}.
The characters of the coset model are connected with the branching functions,
\begin{equation}
  \label{eq:31}
  \chi^{(\mu)}_{\nu}(\tau)=e^{2\pi i \tau (m_{\mu}-m_{\nu})} b^{(\mu)}_{\nu}(\tau),
\end{equation}
where
\begin{equation}
  \label{eq:46}
  m_{\mu}=\frac{\left|\mu+\rho\right|^2}{2(k+g)}-\frac{\left|\rho\right|^2}{2g}.
\end{equation}

The problem of the branching functions construction in the coset models was considered
in  \cite{Dunbar:1992gh}, \cite{Hwang:1994yr}, \cite{lu1994branching}.

Let us return to the example \ref{sec:regul-embedd-a_1} and consider the affine extension of the injection
$A_1\subset B_2$.
Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.
The set $\Delta^{+}_{\bot}$ of the orthogonal positive roots with the zero projection
on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.

Using the definition (\ref{fan-defined}) we get the fan
$\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$
with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
We restricted the computation to the twelfth grade.
\begin{figure}[h!bt]
  \centering
  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

Consider the level one module $L^{\left( 1,0;1;0 \right)}_{\hat{B_2}}$  with the highest weight $w_1=(1,0;1;0)$,
where the finite part coordinates are in the orthogonal basis $e_1,e_2$.

The set of anomalous weights for this module up to the sixth grade is presented in the Figure \ref{fig:affine_B2_anom_point}.
In the grade zero it is exactly the set of the anomalous weights for the embedding of
the classical Lie algebras $A_1\subset B_2$ depicted in the  Figure \ref{fig:B2_A1}.
The weights $\omega (w_1+\rho)-\rho$ are marked by crosses if $\epsilon(\omega)=1$ and by circles otherwise.
Simple roots of the classical subalgebra $B_2$ are grey and grey diagonal plane corresponds to the Cartan subalgebra
of the embedded algebra $\hat{A}_1$.

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of $L^{(1,0;1;0)}_{\hat B_2 }$.
  The weights in the zero grade can be seen in the Figure \ref{fig:B2_A1}}.
  \label{fig:affine_B2_anom_point}
\end{figure}

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to
$P_{\hat{A_1}}$ and find the dimensions of the corresponding
$\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj} up to the twelfth grade.
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}
